Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-09-21 writeup/RochatEtal_ResponseToReviewers.tex

\item {\it In the bottom paragraph on P.10, the authors emphasized that "At scales larger
than 20km, the April and October spectra based on hourly velocity snapshots are
nearly indistinguishable from each other". This emphasis appears to be contradictory
to the statements in other places of the manuscript that the seasonality of subinertial
submesoscale flows is strong (e.g., those relating to Figure 1b-c and Figure 2).}\\

    \bdp
        We agree that the emphasis on the similarity of hourly spectra can appear
        contradictory. Those spectra (now Figure 4c
        and supporting information) are similar because both submesoscale sub-inertial
        and super-inertial flows undergo a strong seasonal cycle that is out of
        phase --- there is a phase cancellation and the spectra based on hourly
        data are indistinguishable within errorbars. In any event, we removed
        that sentence from the text. The new Figure 4 should convey
        the phase cancellation idea more effectively.
    \edp

\item {\it Does the mesoscale eddy variability in the Kuroshio Extension region of the model
have a similar energy level as those in the along-track altimeter data? This point
is worth mentioning as it impacts on the relative importance between the instability-induced
turbulence versus inertia-gravity waves.}

  \bdp
      The model smoothed fields have EKE levels similar to across-track (JASON II)
      geostrophic EKE and gridded geostrophic EKE. We included this stantement with
      the area-averaged EKE. Thanks for pointing this out.
  \edp

@@

\item {\it (Figure 2) Is the mean of the strain rate zero? Is the mean of the divergence zero? The
        variance should be used rather than the root-mean-squared (RMS).}

        \bdp
            At every snapshot, the horizontally-averaged divergence is nearly zero;
            the strain rate horizontal average is not zero, because by definition
            $\alpha \ge 0$. The (normalized) RMS better characterizes the the bulk
            gradient Rossby number of the flow.
        \edp

\item {\it (Figure 2) What is the sensitivity of the estimates to the stencil type? See Arbic et al.
        paper describing this sensitivity for satellite altimetry.}

        \bdp
            Wider stencils are more accurate because their order of accuracy is
            higher. To asses the error of centered second-order scheme we periodized
            our domain
        \edp

### 2016-09-21 writeup/rocha_etal.tex
Small comments and corrections

\begin{abstract}
    We present model-based evidence of
    vigorous modulation of near-surface dynamics at submesoscales
    (10-100 km) in the Kuroshio Extension. Consistent with recent studies, deep late-winter mixed layers
    are prone to baroclinic instabilities, and submesoscale turbulence
    prevails in late winter/early spring. Summertime
    re-stratification weakens submesoscale turbulence and enhances submesoscale inertia-gravity
     waves near the surface. In the Kuroshio Extension,
    inertia-gravity waves strongly dominate the submesoscale surface kinetic energy and
    sea-surface height (SSH) variance in late summer/early fall, with implications for
    the accuracy of surface geostrophic currents diagnosed from SSH measured by
    high-resolution
    satellite altimeters.
\end{abstract}

@@

To study seasonal variations in the upper-ocean dynamics, we focus on the northwest
Pacific, in the vicinity of the Kuroshio
Extension, where previous studies have shown strong mesoscale and submesoscale seasonality
\citep{sasaki_etal2014,qiu_etal2014}.
We analyze a sub-domain of the LLC4320 and LLC2160 simulations of about 2000 km$^2$
spanning 155-175$^\circ$E; 25-40$^\circ$N (Figure \ref{fig1}a). The stratification
in this mesoscale-rich subtropical region undergoes a vigorous seasonal cycle: wintertime-enhanced
small-scale turbulence de-stratifies the upper ocean, yielding mixed layers
deeper than 200 m to the north (Figure \ref{fig1}b). Summertime re-stratification yields mixed layers shallower
than 40 m (Figure \ref{fig1}c).
Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supporting information).

>>>>

\begin{abstract}
    We provide model-based evidence of
    vigorous modulation of near-surface dynamics at submesoscales
    (10-100 km) in the Kuroshio Extension. Consistent with recent studies, deep late-winter mixed layers
    are prone to baroclinic instabilities, and submesoscale turbulence
    prevails in late winter/early spring. Summertime
    re-stratification weakens submesoscale turbulence and enhances submesoscale inertia-gravity
     waves near the surface. In the Kuroshio Extension,
    inertia-gravity waves strongly dominate the submesoscale surface kinetic energy and
    sea-surface height (SSH) variance in late summer/early fall, with implications for
    the accuracy of surface geostrophic currents diagnosed from SSH measured by
    high-resolution satellite altimeters.
\end{abstract}

@@

To study seasonal variations in the upper-ocean dynamics, we focus on the northwest
Pacific, in the vicinity of the Kuroshio
Extension, where previous studies have shown strong mesoscale and submesoscale seasonality
\citep{sasaki_etal2014,qiu_etal2014}.
We analyze a sub-domain of the LLC4320 and LLC2160 simulations of about 2000 km$^2$
spanning 155-175$^\circ$E; 25-40$^\circ$N (Figure \ref{fig1}a). The stratification
in this mesoscale-rich subtropical region undergoes a vigorous seasonal cycle: wintertime-enhanced
small-scale turbulence de-stratifies the upper ocean, yielding mixed layers
deeper than 200 m to the north (Figure \ref{fig1}b). Summertime re-stratification yields mixed layers shallower
than 40 m (Figure \ref{fig1}c).
Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supporting information). Model smoothed
fields have eddy kinetic energy (EKE) levels ($0.041$ m$^2$ s$^{-2}$) similar to Jason II across-track
geostrophic EKE ($0.036$ m$^2$ s$^{-2}$) and gridded geostrophic EKE ($0.032$ m$^2$ s$^{-2}$).
